---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# outlookMailer

<!-- badges: start -->
<!-- badges: end -->

The goal of outlookMailer is to create an R interface between Microsoft Outlook and R, to compose messages from R using Outlook's native window.

## Installation

### Requirements

```{r}
remotes::install_github('omegahat/RDCOMClient')
```

### The package

You can install the released version of outlookMailer from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
install.packages("outlookMailer")
```

## Example

The package wraps the COM interface to Microsoft Outlook with user-friendly R functions.

```{r exemple, eval=FALSE}
library(outlookMailer)

# Create a connection to Outlook
con <- connect_outlook()

# Create a message and show it
msg <- create_draft(con, 
                    addr_to = 'foo@bar.com', 
                    body_plain = 'Body of the message', 
                    use_signature = TRUE,
                    show_message = FALSE)

# Show the message
msg$Display()

# Send the message (caution!)
# msg$Send()

# Close and save to drafts
close_draft(msg, save = TRUE)

```

